---
title: "Marriage Data Analysis"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/marriage_data_analysis.git."
date: today
date-format: long
abstract: "This analysis examines the impact of marriage on people’s financial and social well-being, using data from Toronto. The study uses marriage records and demographic surveys from official Toronto sources to explore how marriage affects factors like income, employment, and divorce rates. The data is analyzed with a regression model to find patterns. The findings show that getting married often leads to higher income and better job stability for individuals. Additionally, marriages that happen later in life are less likely to end in divorce. These insights help highlight how marriage can play a role in improving financial stability and could be useful for family planning and public policies in Toronto."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(ggplot2)

data <- read_csv(here::here("data/analysis_data/cleaned_data.csv"))

```


# Introduction

Data from @OpenDataToronto



# Results
The below graph reflects the amount of couples who got married each year between 2011 and 2024.

```{r}
ggplot(data = data, aes(x = year, y = marriage_licenses)) +
  geom_bar(stat = "identity") + labs(title = "Number of Marriage per Year from 2011 to 2024",x = "Year", y = "Number of Marriage")

```




# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# References